---
title: "SQL Session"
author: "Insight"
date: "06/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(readxl)
getwd()
#install.packages("sqldf")
library(sqldf)

Orders <- read_excel("P1-SuperStoreUS-2015.xlsx", 
    sheet = "Orders")


Returns <- read_excel("P1-SuperStoreUS-2015.xlsx", 
    sheet = "Returns")

Users =read_excel("P1-SuperStoreUS-2015.xlsx", 
    sheet = "Users")
```




# Practice
1.)	Select different states or provinces  and their  corresponding country?

```{r}

sqldf("Select distinct State_or_Province, Country 
      from Orders
      where State_or_Province like 'A%m%'
      order by State_or_Province  asc
      ")
```


2.)	To get list of  product sub-category, Order ID 
when customer segment is Small Business?


```{r}
df=sqldf("Select Product_Sub_Category, Order_ID , Customer_Segment
      from Orders 
      where Customer_Segment in ('Small Business','Corporate')
      and Order_ID > 87000
      order by Order_ID")
write.csv(df,"data1.csv")
df
```

3.)	To find the list of Order ID where order priority is critical ?


```{r}
sqldf("Select Order_ID from Orders where Order_Priority='Critical'")
```

4.)	To get Order ID where order priority is not low?

```{r}
sqldf("Select Order_ID from Orders where not Order_Priority='Low' ")
```

5.)	To get profit where customer segment is Consumer?

```{r}
sqldf("	Select Profit from Orders where Customer_Segment='Consumer' ")
```

6.)	To get Order Id, Customer segment and profit, sorted by “Profit”

```{r}
sqldf("Select Order_ID, Customer_Segment from Orders order by Profit")
```

7.)	To get the maximum profit value 

```{r}
sqldf("Select  Profit from Orders where 
      Profit not in (Select  max(Profit) from Orders) order by Profit desc ")
```


8.)	To get the average profit

```{r}
sqldf("Select avg(Profit) from Orders")
```

9.)	To get Order Id, Product Name where status is “returned”

```{r}
sqldf("Select Orders.Order_ID, Orders.Product_Name 
      from Orders 
      inner join Returns 
      on Orders.Order_ID= Returns.Order_ID")
```

10.)	To get customer id and their corresponding manager name

```{r}
sqldf("Select count (Orders.Customer_ID),Users.Manager 
      from  Orders 
      left join Users on Orders.Region=Users.Region
      group by Users.Manager ")

```


```{r}
sqldf("Select u.Manager as Manager_Name ,count(o.Customer_ID) as Count_of_Customers
      from Users as u
      left join Orders as o
      on o.Region=u.Region
      group by u.Manager ")
```



11.)	To get the list of number of customers from each Region


```{r}
sqldf("Select count(Customer_ID),  Region from Orders group by Region")

```