---
title: "DPA"
author: "Insight"
date: "16/12/2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

 + What is R markdown
 + How to make R markdown
 + R Markdown Cheatsheet 
    + https://rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf
    
 

## Installing all libraries in one command


  + install.packages(c("dplyr", "sqldf","ggplot2",arules", "car", "caTools", "data.table", "forecast", "glmnet", "party", "partykit", "rattle", "Rcpp", "RGtk2", "rpart.plot"))
  
  + http://bit.ly/insightdpa



## Dataframes

```{r echo=TRUE,message=FALSE}
## creating a data frame

empid<- c(21,23,31,62,02); #empid
empname<- as.character(c("A","B","C","D","E"));#empname
desig<- as.factor(c("RM","SMM","ASM","RM","SM"));#desig
design<-factor(desig,levels=c("ASM","RM","SMM"), ordered=TRUE)

db<-as.Date.factor(c("1999-02-02","1998-02-02","1997-02-02","1996-02-02","1995-02-02"))
#db
salary<- c(20000,23000,25000,240000,25000);#salary
region<-as.factor(c("N","S","S","E","W"));#region

employee<- data.frame(empid,empname,desig,db,salary,region,stringsAsFactors = F);employee
```

## Functions used to describe dataframes
```{r echo=TRUE}
str(employee)

dim(employee)

ncol(employee)

nrow(employee)

summary(employee)

names(employee)

class(employee)

mean(employee$salary) # to find the mean length
```

## Basic graphical analysis
```{r echo=T}
library(ggplot2)
ggplot(employee,aes(salary))+geom_histogram()
```

## DPLYR vs SQLDF

  + Both libraries help in filtering of data
  + SQLDF is for programmers with an experience of SQL
  + DPLYR is made for R

## Practice with Filtering of Data
```{r, echo=TRUE}
data=read.csv("auto-mpg.csv")
library(dplyr)
#1 # to find cars whose miles per gallon > median mpg
data %>%  select(car.name,mpg) %>% filter(mpg, mpg > 23.00) 
```

## 2 Finding mean mpg for each cylinder
```{r, echo=TRUE}
data %>% 
  group_by(cylinders) %>%
  summarise(mean_mpg = mean(mpg, na.rm = TRUE))  
```

## 3 calculate mean, min, max and sd of mpg and wt rates by number of cyl 
```{r, echo=TRUE}
data %>%
  group_by(cylinders) %>%
  summarise_each(funs(mean(., na.rm = TRUE), 
                      min(., na.rm = TRUE), 
                      max(., na.rm = TRUE), 
                      sd(., na.rm = TRUE)), 
                 mpg, weight)
```

## 4 calculate mean mpg and weight by number of cylinders 
sumarise_each - applies the same function to multiple columns 
```{r, echo=TRUE}
data %>%
  group_by(cylinders) %>%
  summarise_each(funs(mean(., na.rm = TRUE)), mpg, weight)
```

## 5 count number of cars with each number of cylinders and put in descending order 
```{r, echo=TRUE}
data %>%
  group_by(cylinders) %>%
  summarise(cyl_count=n()) %>%
  arrange(desc(cyl_count))
```


## GGPlot Practice
```{r echo=TRUE}
irisdata=read.csv("IRIS.csv")
(Sepal_data <- ggplot(data=irisdata, aes(x = sepal_length, y = sepal_width)) + geom_point(aes(color=species, shape=species)) +
  xlab("Sepal Length") +  ylab("Sepal Width") +
  ggtitle("Sepal Length-Width"))

(Petal_Data= ggplot(data=irisdata, aes(x = petal_length, y = petal_width)) + geom_point(aes(color=species, shape=species)) +
  xlab("Petal Length") +  ylab("Petal Width") +
  ggtitle("Petal Length-Width"))

(box=ggplot(irisdata,aes(petal_length,sepal_length))+geom_smooth()+geom_boxplot()+facet_grid(~species)+
  ggtitle("Boxplots of petal length vs sepal length"))


(speciesvsSLength=ggplot(irisdata,aes(species,sepal_length))+geom_point()+geom_jitter() +
  ggtitle("Species wise Sepal Length"))

ggplot(irisdata,aes(species,sepal_width))+geom_point()+geom_jitter()+
  ggtitle("Species wise Sepal Width")


ggplot(irisdata,aes(species,petal_length))+geom_point()+geom_jitter()+
  ggtitle("Species wise Petal Length")

ggplot(irisdata,aes(species,petal_width))+geom_point()+geom_jitter()+
  ggtitle("Species wise Petal Width")


```

## QQ plot

```{r echo=TRUE}
library (tseries)

jarque.bera.test(data$mpg) 

qqnorm(data$mpg, pch = 1, frame = FALSE)
qqline(data$mpg, col = "steelblue", lwd = 2)


```


## Linear Regression - Reading Data
```{r echo=TRUE}
library(readxl)
myData <- read_excel("petrol diesel data.xls")
df<- myData
#View(df)
names(df)
```

## Linear Regression - Renaming columns
```{r echo=TRUE}
colnames(df)[colnames(df)=="Petrol (MT)"]<-"petrol" 			    # Renaming the columns	
colnames(df)[colnames(df)=="HSD (MT)"]<-"diesel"			    # Renaming the columns	
colnames(df)[colnames(df)=="GDP 99-00 price (Rs. million)"]   <-"gdp"	        # Renaming the columns
colnames(df)[colnames(df)=="Real Pr HSD (Rs/Lit)"]<-"realDies"	      # Renaming the columns
colnames(df)[colnames(df)=="Real Pr Petrol (Rs/Lit)"]<-"realPet"	      # Renaming the columns

names(df)
head(df)
```

## Linear regression - selecting useful columns only
```{r echo=TRUE}
df <-df[c(2,3,4,5,6)] 						                    # Select the column by index, 
head(df)
```

## Linear Regression - understanding
```{r echo=TRUE}
options (scipen=99999)
##Regression
reg<-lm(petrol~gdp+realPet+realDies, data=df)        #Petrol
summary(reg)
```

```{r}
reg<-lm(petrol~gdp+log(realPet), data=df)        #Petrol
summary(reg)
```